The imprint of global magma oceans on exoplanet demographics

### 2022-11-28 src/tex/ms.tex
describe planetary sample selection cuts
Separate subsections on star and planet sample

\subsection{Synthetic star and planet sample}
The first step in our analysis is to generate a synthetic sample of stars and planets.
First, we created a stellar population based on the observed population in the solar neighborhood, to which we then assign planetary systems based on occurrence rates derived from the \kepler mission.

@@

\subsubsection{Orbital and bulk properties of the planet sample}
Next, we assigned planetary systems to the synthetic stellar sample.
The orbital parameters and bulk properties of these simulated planets are informed by statistics from the \kepler mission; we adopted the planetary occurrence rates recently derived in \citep{Bergsten2022}.
Following \citep{Youdin2011a}, their inferred occurrence rate density can be expressed in the form
\begin{equation}
    \frac{\mathrm{d}^2n}{\mathrm{d}R \, \partial P} = F_0 C_n g(R, P),
\end{equation}
where $F_0$ ...
\todo[inline]{GALEN: Describe underlying planet occurrence rates of synthetic population, its Mstar dependency, any caveats or assumptions.}

\begin{note}
    ...
    In this study, we consider only rocky planets with a maximum mass of \SI{2}{\Mearth}. % (Turbet+2020 goes only up to 2 Mearth)

    ...
    To assign masses to our planets, we use the theoretical mass-radius relationship derived in \citet{Zeng2016}.
    The default relation our planets follow is one assuming a pure $\mathrm{MgSiO_3}$ composition. 
    \todo[inline]{JUSTIFY this choice}
    This represents the baseline bulk density before any magma ocean-related effects are applied.
\end{note}

>>>>

\subsection{Synthetic star sample}
The first step in our analysis is to generate a synthetic sample of stars and planets.
First, we created a stellar population based on the observed population in the solar neighborhood, to which we then assign planetary systems based on occurrence rates derived from the \kepler\ mission.

@@

\subsection{Synthetic planet sample}
Next, we assigned planetary systems to the synthetic stellar sample.
The orbital parameters and bulk properties of these simulated planets are informed by statistics from the \kepler\ mission.

\subsubsection{Planet occurrence rates in orbital period and radius}
We adopted the planetary occurrence rates recently derived in \citep{Bergsten2022}.
Following \citep{Youdin2011a}, their inferred occurrence rate density can be expressed in the form
\begin{equation}
    \frac{\mathrm{d}^2n}{\mathrm{d}R \, \partial P} = F_0 C_n g(R, P),
\end{equation}
where $F_0$ ...
\todo[inline]{GALEN: Describe underlying planet occurrence rates of synthetic population, its Mstar dependency, any caveats or assumptions.}

\subsubsection{Eccentricities, orbital inclinations, and planet masses}

...

To assign masses to our planets, we use the theoretical mass-radius relationship derived in \citet{Zeng2016}.
The default relation our planets follow is one assuming a pure $\mathrm{MgSiO_3}$ composition.
\todo[inline]{JUSTIFY this choice}
This represents the baseline bulk density before any magma ocean-related effects are applied.
...

\subsubsection{Sample selection}
\begin{note}
    ...
    In this study, we consider only rocky planets with masses \SIrange{0.1}{2}{\Mearth}. % (Turbet+2020 covers only 0.1 to 2 Mearth)
    As we are interested in the effects of runaway greenhouse phases of planets with volatiles and atmosphere, we further excluded lava worlds with extremely high instellation that does not allow long-term preservation of an atmosphere.
    We thus removed all planets with an instellation $S > \SI{2000}{\watt\per\square\meter}$.
\end{note}
